The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2017-03-08 manuscript/manuscript.Rnw
fix pubmed_to_grid latex escape

To identify genes which have evidence of association with adverse
pregnancy outcomes and other placenta-relevant terms of interest, we
used the “pubmed_to_grid” component of
Function2Gene~\cite{Armstrong2008:function2gene} which conducts a term
by gene search of PubMed results.

>>>>

To identify genes which have evidence of association with adverse
pregnancy outcomes and other placenta-relevant terms of interest, we
used the “pubmed\_to\_grid” component of
Function2Gene~\cite{Armstrong2008:function2gene} which conducts a term
by gene search of PubMed results.
